% Example usage for Spaghetti Bolognese
\recipeheader{SPAGHETTI BOLOGNESE}

\recipedesc{Bolognese sauce, known in Italian as ragù alla Bolognese, is a meat-based sauce originating from Bologna, Italy. In Italian cuisine, it is customarily used to dress "tagliatelle al ragù" and to prepare "lasagne alla bolognese".}

\recipemeta{4}{25 mins}{40 mins}{Beginner}

\begin{recipe}

\begin{ingredients}
	\item{1 tbsp olive oil}
	\item{20g butter}
	\item{2 brown onions, halved,\\ finely chopped}
	\item{2 garlic cloves, crushed}
	\item{500g beef mince}
	\item{145g (1/2 cup) tomato paste}
	\item{250mL (1 cup) dry red wine}
	\item{2 x 400g cans of diced tomatoes}
	\item{1 tbsp dried oregano}
	\item{3 dried bay leaves}
	\item{Salt and freshly ground\\ black pepper}
	\item{1/3 cup fresh parsley, loosely packed, coarsely chopped}
	\item{375g dried thin spaghetti}
	\item{80g parmesan, to serve}
\end{ingredients}

\begin{instructions}
\item Heat oil and butter in a large saucepan over medium-high heat. Add onion and garlic and cook, stirring, for 3 minutes or until onion softens. Add the mince and cook, stirring with a wooden spoon to break up any lumps, for 5 minutes or until the mince changes color.

\item Add the tomato paste, wine, tomato, oregano and bay leaves, and bring to the boil. Reduce heat to medium and simmer, stirring occasionally, for 1 hour or until sauce thickens. Taste and season with salt and pepper. Stir in the parsley.

\item Meanwhile, cook the spaghetti in a large saucepan of salted boiling water following packet directions until al dente. Drain.

\item Divide the spaghetti among bowls and spoon over bolognese sauce. Grate over the parmesan and serve immediately.

\end{instructions}

\recipenote{You can freeze this bolognese sauce for up to 2 months. Cool to room temperature, then place individual portions or whole quantity in airtight containers or freezer bags and expel air. Label, date and freeze. Place in the fridge overnight to thaw.}

\end{recipe}